---
title: "The use of farspack package "
author: "Elena Alexandrova"
date: "2019-01-01"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# General information
This package is a project required by Coursera's Building R Packages course. The code for functions and data file included in this package were provided by the course.

```{r get_my_pack} 
library(farspack)
```

## The purpose of package
The package contains five functions for processing Fatality Analysis Reporting System (FARS) files from National Highway Traffic System Administration (https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars). The outcome of package are summaries and plots of traffic accidents for each state in USA.

### Set root directory for knitr
The package contains original data set included for showing example of loading and analyzing raw data. The package knitr requires to set a root directory in order to access the included dataset and knit vignette to html.

```{r, setup, include=FALSE, echo=FALSE}
require("knitr")
opts_knit$set(root.dir = "~/Desktop/R program spec/R prog Course 3/farspack/inst/extdata")
```

### Give a name to data file
The function creates a file name for the specific year and prints it.

```{r, name, echo = TRUE, eval = TRUE}
filename <- make_filename(2013)
```

### Read .csv file
The function loads US FARS data and turns a flat file into the data frame.

```{r, year_read, echo = TRUE, eval = TRUE}
subset_2013 <- fars_read(filename)
```

### Create a file for the specific date
The function creates a subset that contains the accidents for given years sorted by month.

```{r, years_read, echo = TRUE, eval = TRUE}
all_years <- fars_read_years(years = list(2013,2014,2015))
```

### Monthly summary of accidents for years of interest
The function is summarising  the number of accidents per month for each particular year.

```{r, accidents_summary, echo = TRUE, eval = TRUE}
all_res <- fars_summarize_years( years = 2013:2015)
```

### Geo map with location of incidents for specific year
The function builds a geographical map of the state with plotted traffic accidents. Each point represents a single case from the FARS data file for one specific year.
```{r, accidents_map, echo = TRUE, eval = TRUE, warning = FALSE}
map <- fars_map_state(10,2013)
```




